Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-26 tex/results.tex
results.tex

For the case of aspect ratio four (AR=4) we obtain the smallest error using the uniform
mesh. Since we count with the mesh provided by the authors, and knowing that our computation 
for the mode $E^{\parallel}_{100}$ compares well with their computations, we attempted to 
validate our simulations with their experimental results (red curve on paper), as well 
as to replicate their simulations (green curve on paper) on Figure 2a of their paper.
Figure 2a of Ellis et al, presents measured and simulated reflectance of SiC pillar
arrays with a 500 nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated size of the pillar.

Using \pygbe we compute the extinction cross section of an isolated SiC pillar (AR=4)
with no substrate, submerged in air under a constant electric field in the z-direction, 
and rotate the orientation of the pillar to match the angle of incidence (see Figure \ref{fig:ellis_ang_inc}).
In Figure \ref{fig:pygbe_vs_exp_2a} we present 
comparison of our simulations and the experimental results from Ellis et al. There is a 
difference in the peaks wavelength that is noticeable. This could be attributed to the
fact that in their experiments the separation between pillars is of 500 nm, which implies
there are coupling effects that in our simulations are not contemplated.

@@

Since our simulations do not count for coupling effects, we can not strictly imitate 
the conditions to validate our solver. However, from Figure S4 on the supplementary 
material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^-1$. Therefore as a \textit{first order correction} we can 
subtract this value from our simulations to count for coupling effects. In Figure 
\ref{fig:val_2a} we present the result after applying the correction for coupling effects.
It is worth mentioning that the far left (837 cm$^-1$) and far right (964 cm$^-1$) peaks 
on Ellis results, are peaks associated with zone-folded LO (longitudinal) phonons, in 
particular P1 (837 cm$^-1$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
do not discuss this result into detail, but they concentrate their analysis on the peaks
that happen between 864–961 cm$^-1$

>>>>

The results of Figure 2a on Ellis et al. were obtained on a pillar of aspect ratio $AR=4$. For this case,
we count with the mesh provided by the authors. We also know that our computation 
for the mode $E^{\parallel}_{100}$ compares well with theirs (percentage error 0.16$\%$), therefore we
attempted to validate our simulations with their experimental results (red curve on paper), as well 
as to replicate their simulations (green curve on paper).
Figure 2a of Ellis et al, presents measured and simulated reflectance of SiC pillar
arrays with a 500 nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated size of the pillar.

Using \pygbe we compute the extinction cross section of an isolated SiC pillar (AR=4)
with no substrate, submerged in air under a constant electric field in the z-direction, 
and rotated the orientation of the pillar to match the angle of incidence used on Ellis et al. (see Figure \ref{fig:ellis_ang_inc}).
In Figure \ref{fig:pygbe_vs_exp_2a} we present a 
comparison of our simulations and the experimental results from Ellis et al. There is a 
difference in the peaks wavelength that is noticeable. This could be attributed to the
fact that in their experiments the separation between pillars is of 500 nm, which implies
there are coupling effects that in our simulations are not contemplated.

@@

Since our simulations do not count for coupling effects, we can not strictly imitate 
the conditions to validate our solver. However, from Figure S4 on the supplementary 
material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^-1$. Therefore, as a \textit{first order correction} we can 
subtract this value from our simulations to count for coupling effects. In Figure 
\ref{fig:val_2a} we present the result after applying the correction for coupling effects.
It is worth mentioning that the far left (837 cm$^-1$) and far right (964 cm$^-1$) peaks 
on Ellis results, are peaks associated with zone-folded LO (longitudinal) phonons, in 
particular P1 (837 cm$^-1$) is not infrared active \cite{ellis2016}. Ellis and coworkers, 
do not discuss this result into detail, but they explain that these peaks go beyond the scope of the work, 
they concentrate their analysis on the peaks that happen between 864–961 cm$^-1$
